### 2019-10-01 conflog.tex
makes various updates

\subsubsection{Getting to the Conference}
The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance. Thus we have budgeted to include transportation provided by Peoria Charter. We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana. For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes. This bus route, the 22 Illini, can take attendees directly to the Union from the hotel. It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus. Lyft and Uber are available as well for attendees that choose to use those services. A map of the bus route is in Appendix E: Campus Map of Locations on page \pageref{appendix:map}.

>>>>

\input{conftrans}

### 2019-10-01 management.tex
makes various updates

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-chee.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
$\textbf{Technical Subcommittee Chair - Gwen Chee}$\\
	Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr. Kathryn Huff in the ARFC group. Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex. She also serves as the president of the UIUC chapter of Women In Nuclear (WIN). Under her leadership, WIN-UIUC was honored with the Best Student Chapter award at the WIN National Meeting in 2019. She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
\end{minipage}

>>>>

\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-chee.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
$\textbf{Technical Subcommittee Chair - Gwendolyn Chee}$\\
	Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr. Kathryn Huff in the ARFC group. Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex. She also serves as the president of the UIUC chapter of Women In Nuclear (WIN). Under her leadership, WIN-UIUC was honored with the Best Student Chapter award at the WIN National Meeting in 2019. She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
\end{minipage}

### 2019-10-01 proglog.tex
makes various updates

Brewery tours are staple social event and tour at the ANS Student Conference. Champaign-Urbana has several popular local breweries that give tours and tastings at their facilities. Due to this, we will be able to expand the number of attendees that can go on these tours over previous conferences. These will require sign up before the conference and we expect spots to fill up quickly.\\

\noindent{\begin{minipage}{0.5\textwidth}
	% \centering
	\textbf{Riggs Brewery Tour}\\
For 21+ attendees, two tours of a local brewery will be included in our tours list Thursday afternoon from 3-5pm. Find out how Riggs makes their beer and taste test it along the way. Each tour will last approximately one hour and accommodates up to 20 people per tour. Riggs is located in east Urbana. Transportation to and from the brewery will be provided. 
\end{minipage}
\begin{minipage}{0.55\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{riggs.jpg}
	\captionof{figure}{Riggs Brewery}
\end{minipage}}

@@

\noindent{\begin{minipage}{0.5\textwidth}
	\textbf{NPRE Lab Tours}\\
Attendees will be able to take a tour of the various NPRE labs on campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. After, they will walk across the Engineering Quad to the Center for Plasma-Material Interactions (CPMI) where students conduct experiments on the stellerator-tokamak, HIDRA. There are also many other historical artifacts on display for participants to see. This tour will depart from the front entrance of the Illini Union.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{creek.png}
	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
\end{minipage}}
\\

>>>>

Brewery tours are staple social event and tour at the ANS Student Conference. Champaign-Urbana has several popular local breweries that give tours and tastings at their facilities. Due to this, we will be able to expand the number of attendees that can go on these tours over previous conferences. These will require sign up before the conference and we expect spots to fill up quickly. Attendees will have the option of choosing one brewery tour.\\

\noindent{\begin{minipage}{0.5\textwidth}
	% \centering
	\textbf{Riggs Brewery Tour}\\
For 21+ attendees, two tours of a local brewery will be included in our tours list Thursday afternoon from 11-1pm. Find out how Riggs makes their beer and taste test it along the way. Each tour will last approximately one hour and accommodates up to 20 people per tour. There will be a variety of food trucks at the brewery to purchase lunch. Riggs is located in east Urbana. Transportation to and from the brewery will be provided. 
\end{minipage}
\begin{minipage}{0.55\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{riggs.jpg}
	\captionof{figure}{Riggs Brewery}
\end{minipage}}

@@

\vspace{0.5cm}
\noindent{\begin{minipage}{0.5\textwidth}
	\textbf{NPRE Lab Tours}\\
Attendees will be able to take a tour of the various NPRE labs on campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. After, they will walk across the Engineering Quad to the Center for Plasma-Material Interactions (CPMI) where students conduct experiments on the stellerator-tokamak, HIDRA. There are also many other historical artifacts on display for participants to see. This tour will depart from the front entrance of the Illini Union.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{creek.png}
	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
\end{minipage}}
\\
